Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-07 Paper/paper.tex
Quick todo addition

\subsection{Template Files}
In order to get developers up and running as quickly as possible, we've included a couple template files below that will get them started out.

>>>>

\subsection{Template Files}
\todo{Flesh out this section}
In order to get developers up and running as quickly as possible, we've included a couple template files below that will get them started out.
